### 2019-07-19 manuscript/response.tex

\hfill \today.

Dear Dr. Schoen and Reviewers,

\medskip
Thank you very much for your close reading of our manuscript and supportive comments. We appreciate your constructive suggestions, each of which we address below. You will find a great difference in the number of models that we have fitted for the revision based on reviewer suggestions (originally 12, now 29, with a special supplementary figure to enable easy visualization). There are two main reasons for this sizable increase.

First, we performed additional work to address a key concern from all referees about the transition symmetry among the hidden states. 
Briefly, we found that is relevant to have asymmetric hidden state rates and, in our case, it increased the differences among net diversification rates. 
We added and altered the text to reflect these additional analyses.

Second the time since the first version allowed us to mull over an important issue. 
Specifically, we wondered whether increasing the state space from two-states (single-trait) to three-states (two traits) explains the data better (and how they ought to be best compared). 
This trait-coding question could not be addressed directly by model comparison, because the two-state and three-state models need different input (i.e. (0,1) versus (0,1,2)). 
The species and the tree are identical, however, and our intuition indicated that they should carry the same biological evidence despite a particular coding input. 
During this revision, with the help of Sergei Tarasov's recent paper \citep{tarasov_2019}, we found a way to recode the three-state models to make them equivalent to the two-state models (these are called ``lumped models"). 
This equivalency enables comparison of two-state and three-state models, and assessment of their relative explanatory value after adding key trait information and states in diversification analyses.
We also revised the original dataset (thanks to the suggestion of Reviewer 1), we were able to correct discrepancies with a previous dataset, as well as add more data (now 651 taxa).

We hope the changes and the new models are satisfactory to all of you.

@@

\medskip
Sincerely,

Rosana Zenil-Ferguson, Gordon Burleigh, Boris Igi\'c, Itay Mayrose, and Emma Goldberg

### 2019-07-19 manuscript/main.tex
REVISION VERSION (JULY 19, 2019) NEW PHYTOLOGIST NPH-MS-2019-29554.R1
- Note: final submission will require all figures to be uploaded separately
- Figures are currently spread across two directories with some stale versions
- Author Contributions is commented out, but will be populated in the next commit
- There are FIXME marks remaining in a few places
- Author contributions copied from Rosana's email and adapted to narrative form

%--------------------------------------------------
\section{Acknowledgements}
%--------------------------------------------------
Special thanks to Bob Thomson for donating computational resources that made possible testing the convergence of the models. 
We also thank Sergei Tarasov for clarifying lumpability concepts, and Carrie Tribble for troubleshooting some ancestral estimate figures. 
The computing resources were provided by the Minnesota Supercomputing Institute (MSI) at the University of Minnesota.
This work was supported by the National Science Foundation grants DEB-1655478 (to EEG and IM), NSF DEB-1655692 \& NESCent sabbatical scholar award EF-0905606 (to BI), and the Israel Science Foundation 961/17 (to IM). %IM: #32
We thank Dan Schoen and three anonymous reviewers for providing uncommonly thoughtful and helpful reviews, as well as Spencer Barrett for continually inspiring our work.

>>>>

%--------------------------------------------------
\section{Acknowledgements}
%--------------------------------------------------
Special thanks to Bob Thomson for donating computational resources that made possible testing the convergence of the models. 
We also thank Sergei Tarasov for clarifying lumpability concepts, and Carrie Tribble for troubleshooting some ancestral estimate figures. 
The computing resources were provided by the Minnesota Supercomputing Institute (MSI) at the University of Minnesota.
This work was supported by the National Science Foundation grants DEB-1655478 (to EEG and IM), NSF DEB-1655692 \& NESCent sabbatical scholar award EF-0905606 (to BI), and the Israel Science Foundation 961/17 (to IM). %IM: #32; ISF funding source not recognized by NP database.
We thank Dan Schoen and three anonymous reviewers for providing uncommonly thoughtful and helpful reviews, as well as Spencer Barrett for continually inspiring our work.

%--------------------------------------------------
%\section{Author Contributions}
%--------------------------------------------------

%B: these are from July 19th, 2019, email from RZF:
RZF, BI, and EEG designed the research; RZF and EEG performed the research; RZF conducted data analyses; RZF, BI, and EEG collected the data; RZF, BJG, WF, BI, EEG were involved in data interpretation; RZF, BJG, WF, BI, IM, and EEG wrote the manuscript.
